Practical implications of HATEOAS on a bridge between LOD and SPARQL

### 2012-02-27 eswc-2012/workshop.tex
section heads
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@121 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
This paper makes two points: 1) SPARQL is a necessity for non-trivial
navigation in Linked Data, 2) The community needs to pay attention to
the HATEOAS constraint of REST and its practical implications for
making a bridge between LOD and SPARQL possible.

@@

>>>>

\begin{abstract}
This paper makes two points: 1) SPARQL is a necessity % TODO: relax 
for non-trivial navigation in Linked Data, 
2) The community needs to pay attention to
the HATEOAS constraint of REST and its practical implications for
making a bridge between LOD and SPARQL possible.

@@

\section{Non-trivial graph traversal}

\section{Finding the way with voiD}
